Estimating Neighborhood Rents with Scraped Data

### 2018-06-05 manuscript/index.Rmd
submission version

The key steps of any data process can be distilled into three tasks: a.) _extract_ a table of interest from a specified origin source, b.) _transform_ it to support the desired analyses and c.) _load_ the transformed data to a storage destination for future use.

In the present case, a program extracts scraped listings observed since the data updated by sending a download request to the scraper's accumulated data in the form of a URL with a suffix indicating the number of hours that passed since the last processing. The processing routine then transforms the data by cleaning up some of the scraped fields and appending spatial information through a multi-step geocoding proces. If address information was successfully scraped from the listing metadata, the script makes a call to Google Maps Geocoding API using this listing feature and a constraint to search within Washington state. When this first step is not successful at geocoding to a specific address or cross-streets, or where there is no address in the listing metadata, we use SmartyStreet's Address Extraction API on the listing's full scraped text to see if an address was mentioned there. We are able to geocode 95\% of listings to some degree of precision, with the vast majority precise at least to Zip9 geography. All listings used in the following analyses are geocoded with precision at least to Zip9 geography. After geocoding the data and ensuring there are no duplicates among the table of new listings, the script loads the processed listings into the existing database.

@@

This study highlights the importance of considering scraped web data for understanding the dynamics of neighborhood rental housing costs. Throughout this work we demonstrate how Craigslist rental housing listings scraped may be used to research the estimated rent for the Seattle market and its neighborhoods. Models

>>>>

The key steps of any data process can be distilled into three tasks: a.) _extract_ a table of interest from a specified origin source, b.) _transform_ it to support the desired analyses and c.) _load_ the transformed data to a storage destination for future use. In the present case, a program extracts scraped listings observed since the data updated by sending a download request to the scraper's accumulated data in the form of a URL with a suffix indicating the number of hours that passed since the last processing. The processing routine then transforms the data by cleaning up some of the scraped fields and appending spatial information through a multi-step geocoding process.

If address information was successfully scraped from the listing metadata, the script makes a call to Google Maps Geocoding API using this listing feature and a constraint to search within Washington state. When this first step is not successful at geocoding to a specific address or cross-streets, or where there is no address in the listing metadata, we use SmartyStreet's Address Extraction API on the listing's full scraped text to see if an address was mentioned there. We are able to geocode 95\% of listings to some degree of precision, with the vast majority precise at least to Zip9 geography. All listings used in the following analyses are geocoded with precision at least to Zip9 geography. After geocoding the data and ensuring there are no duplicates among the table of new listings, the script loads the processed listings into the existing database.

@@

This study highlights the importance of considering scraped web data for understanding the dynamics of neighborhood rental housing costs. Throughout this work we demonstrate how Craigslist rental housing listings scraped may be used to research the estimated rent for the Seattle market and its neighborhoods. Using Bayesian spatial smoothing models further exploit the scraped data's spatial and temporal richness, giving researchers an option for studying rental housing market dynamics on a more granular scale where time is not only considered in terms of trend, but also random shock and seasonality.

Finally, this paper has endeavored (perhaps a little too much...) to provide an example for using scraped rental housing listings for research, but also with to model for how Rmarkdown, Git and GitHub are transformative technologies for our disciplines. There are no free lunches with reproducibility: these open-source technologies demand that we learn how to incorporate them into our work. To the extent that this requires thinking about analysis beyond a userbase of 1, there can be some growing pains. However, there are some positive spillovers beyond improving the _science_ of social science---including new platforms and media for sharing research findings and ideas.
